Seg_sites_rarefaction

### 2024-04-09 manuscript/ms.Rmd
changes prior to moving to doc for final

## Emperical Validation
To validate equations 4 and 5, we simulated genotypic data for two populations with sizes 100 and 1000, each with 100 bi-allelic loci with minor allele frequencies spaced equally between 0.01 and 0.1. We added missing data to each population assigning each locus a missing data rate $R_{mq}$ from a uniform distribution such that $R_{mq} \sim U(0,.3)$, ensuring that overall allele frequencies in each population were maintained. We then used the methods described above to estimate $P({S_{jq}})$ and $E(N_{S})$ and their variances given $\gamma = 30$. For comparison, we also conducted 10,000 random draws of size $\gamma$ from each loci in each population, then calculated $P({S_{jq}})$ and its variance for each locus empirically and $E(N_{S})$ by summing across all 100 loci for each set of draws. We likewise calculated the variance of $N_{S}$ directly across all sets of random draws.

To compare our calculated estimates to the empirical simulations, we used the implementation of the Agresti-Coull [@agrestiApproximateBetterExact1998] method from the R package `binom` [@dorai-rajBinomBinomialConfidence2022] to calculate 95% confidence intervals for each empirical $P({S_{jq}})$. We also used normal approximation to calculate 95% confidence and prediction intervals for $E(N_{S})$ and $N_{S}$ using $\sigma_{E(n_{S})}^{2}$ and the variance directly observed from the simulations, respectively.

# Results
The methods described here for calculating $P({S_{j}})$ and $E(N_{S})$ performed well. Individual $P({S_{jq}})$ values for each locus were within the confidence intervals derived from the simulated values for 97 and 96% of loci from the $n = 100$ and $n = 1000$ populations, respectively (Figure 1). Note that variation along the generally correlated minor allele frequency/$P({S_{jq}})$ axes is due to variations in genotype frequencies in the simulated data for a given minor allele frequency. $P({S_{jq}})$ values estimated using equation 4 account for this adequately.

$E(N_{S})$ values estimated with equation 5 were similarly accurate and were within the 95% confidence intervals produced using the simulated $N_{S}$ for both population sizes (Figure 2). Likewise, the 95% prediction intervals calculated using $\sigma_{E(n_{S})}^{2}$ via equation 7 contained 96.1 and 95.3% of the simulated $N_{S}$ values for $n = 100$ and $n = 1000$, respectively (Figure 2).

@@

Figure 1: The expected probabilities $P({S_{j,a}})$ of observing a segregating site at a locus for loci with different minor allele frequencies. Probabilities are derived from Equation 4 for each locus *a* for population sizes of 100 (left) and 1000 (right), each rarefacted to $n = 30$. Each locus has a random, independent percentage of missing data which varies between 0 and 30. Points are colored depending on if they fell within a 95% confidence level based on 10,000 random re-samplings of each population to 30 individuals.

Figure 2: The expected total number of segregating sites $E(N_{S})$ from populations of either 100 or 1,000 sampled to 30 individuals as calculated via Equation 5 vs that observed from 10,000 random re-samplings to 30 individuals. 95% Confidence and prediction intervals for $E(N_{S})$ are shown, calculated according to Equations 8 and 9. Observed $N_{S}$ values from each re-sample are colored depending on if they fell within the estimated 95% prediction interval. The mean $N_{S}$ across all re-samples is marked with a triangle, colored depending on if it fell within the estimated 95% confidence interval.

>>>>

## Emperical Validation
To validate equations 4 and 5, we simulated genotypic data for two populations with sizes 250 and 2,500, each with 100 bi-allelic loci with minor allele frequencies spaced equally between 0.01 and 0.1. We added missing data to each population assigning each locus a missing data rate $R_{mq}$ from a uniform distribution such that $R_{mq} \sim U(0,.3)$, ensuring that overall allele frequencies in each population were maintained. We then used the methods described above to estimate $P({S_{jq}})$, $E(N_{S})$, their variances, and 95% confidence and prediction intervals for $\gamma = $ 10, 20, ..., 100. For comparison, we also conducted 1000, 2000, ..., 10,000 random draws for each $\gamma$ from every loci in each population, then calculated $P({S_{jq}})$ and its variance for each locus empirically and $E(N_{S})$ by summing across all 100 loci for each set of draws.

To compare our calculated estimates to the empirical simulations, we used the implementation of the Agresti-Coull [@agrestiApproximateBetterExact1998] method from the R package `binom` [@dorai-rajBinomBinomialConfidence2022] to calculate 95% confidence intervals for each empirical $P({S_{jq}})$ derived from the simulations described above.

# Results
The methods described here for calculating $P({S_{j}})$ and $E(N_{S})$ performed well. Individual $P({S_{jq}})$ values for each locus and $\gamma$ from each population were within the 95% confidence intervals calculated from their respective simulations ~95% of the time, with no substantial bias across minor allele frequency or the number of simulations (Figures 1-2), although confidence intervals calculated from simulations with higher $\gamma$ values tended to contain $P({S_{j}})$ slightly more often (Figure S1). Note that variation along the generally correlated minor allele frequency/$P({S_{jq}})$ axes visible in Figure 1 due to variations in genotype frequencies in the simulated data for a given minor allele frequency. Given that the $P({S_{jq}})$ values estimated using equation 4 track the confidence intervals calculated from simulations, this is accounted for adequately.

Calculations of the total number of segregating sites after rarefaction were likewise very similar to those observed via simulating random draws for any $\gamma$ or iteration counts. Specifically, $E(N_{S})$ values calculated via Equation 5 were very close to the mean number of segregating sites in each population after rarefaction (Figure 3, Figure S2). 95% prediction intervals were generally very close to observed 95% quantiles from simulations across $\gamma$ and simulation counts but were consistatntly slightly overestimated on both ends. This is expected given that Equation 9 assumes normality; the actual distribution of $N_{S}$ values are slightly non-normal across samples. Specifically, the medians, but not the means, of the observed samples are therefore slightly above $E(N_{S})$ (Figure S2). Both point estimates of the number of segregating sites and 95% prediction intervals are similarly accurate across a wide range of both $\gamma$ values and simulation counts (Figure 4).

@@

Figure 1: The expected probabilities  of observing a segregating site at each locus ($P({S_{jq}})$) for loci with different minor allele frequencies. Probabilities are derived from Equation 4 for each locus for population sizes of 250 and 2500 rarefacted to either $N = 10$ or $N = 100$, corresponding to $\gamma = 10$ or $\gamma = 100$. Points vary from the trend lines due to the addition of missin data: each locus has a random, independent percentage of missing data which varies between 0 and 30. Points are colored depending on if they fell within a 95% confidence interval based on 10,000 simulated rarefaction trials of each population to each $N$, which is marked for each point with an error bar.

Figure 2: Trends in difference between the mathematically expected probability that a locus segregates after rarefaction $P({S_{jq}})$ and the observed probability of segregation following simulated rarefaction across different rarefaction sizes ($\gamma$), minor allele frequencies, and number of simulated rarefaction events. Loci are colored depending on if the expected probabilities fell within the observed 95% prediction intervals.

Figure 3: The distribution of the total number of segregating sites ($N_{S}$) observed for 10,000 replicate simulated rarefaction trials to either $N = 10$ or $N = 100$ (corresponding to either $\gamma = 10$ or $\gamma = 100$, respectively) for starting population sizes of either $N = 250$ or $N = 2500$. The mathematically expected number of segregating sites ($E(N_{S})$) and 95% prediction intervals on that number are shown with solid yellow or dashed blue lines for each for each distribution.

Figure 4: Trends in the distribution of the total number of segregating sites ($N_{S}$) observed following rarefaction trails across a range of rarefaction sizes ($\gamma$) and number of trials for starting population sizes of either $N = 250$ or $N = 2500$. Horizontal lines on each distribution note 95% quantile limits. The mathematically expected number of segregating sites ($E(N_{S})$) and 95% prediction intervals on that number are shown in yellow error bars to the right of each distribution.

### 2024-04-09 scripts/seg_sites_rarefaction.Rmd
changes prior to moving to doc for final

f1 <- ggplot(F1data[F1data$source == "Mathematical",],
             aes(x = af, y = p)) +
  geom_point(aes(color = in_ci)) +
  geom_errorbar(aes(ymax = upper, ymin = lower)) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  scale_color_manual(values = colors) +
  guides(color = guide_legend(title = "In CI")) +
  ylab(bquote(italic(P*"("*S[jq]*")"))) +
  xlab("Minor Allele Frequency") +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2]))

@@

# Figure 2: Distribution of Nseg vs Eseg for four runs

@@

@@

K100_data <- which(ks == 100 & n_iters == 10000)
F2data_K100 <- prep_f2(seg1 = res_files[[K100_data]]$seg1, 
                       seg2 = res_files[[K100_data]]$seg2, 
                       vseg1 = vseg1$K_100,
                       vseg2 = vseg2$K_100,
                       F1data = F1data_K100,
                       n1 = n1,
                       n2 = n2)

F2data_K10$sum_tab$K <- "gamma * ' = 10'"
F2data_K100$sum_tab$K <- "gamma * ' = 100'"
F2data_K10$all_mcmc_sums$K <- "gamma * ' = 10'"
F2data_K100$all_mcmc_sums$K <- "gamma * ' = 100'"
F2data_K10$pi_tab$K <- "gamma * ' = 10'"
F2data_K100$pi_tab$K <- "gamma * ' = 100'"

F2data_sums <- rbind(F2data_K10$sum_tab, F2data_K100$sum_tab)
F2data_sums$pop <- gsub("n", "N", F2data_sums$pop)
F2data_sums$pop <- paste0("'", F2data_sums$pop, "'")

F2data_mcmcs <- rbind(F2data_K10$all_mcmc_sums, F2data_K100$all_mcmc_sums)
F2data_mcmcs$pop <- gsub("n", "N", F2data_mcmcs$pop)
F2data_mcmcs$pop <- paste0("'", F2data_mcmcs$pop, "'")

F2data_pi <- rbind(F2data_K10$pi_tab, F2data_K100$pi_tab)
F2data_pi$pop <- gsub("n", "N", F2data_pi$pop)
F2data_pi$pop <- paste0("'", F2data_pi$pop, "'")

f2 <- ggplot(F2data_mcmcs, aes(x = nseg)) +
  geom_density() +
  geom_vline(data = F2data_sums, aes(xintercept = nseg), color = colors[1]) +
  geom_vline(data = F2data_pi, aes(xintercept = lower), linetype = "dashed", color = colors[2]) +
  geom_vline(data = F2data_pi, aes(xintercept = upper), linetype = "dashed", color = colors[2]) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  scale_y_continuous(expand = c(0,0)) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank()) +
  xlab(bquote(italic(N[S]))) +
  ylab("Density")

ggsave("Figure2.pdf", f2, height = 10, width = 15)

@@

# Figure 3: var vs difference between estimate and mean of simulations for mcmc and k

@@

# Figure S1: gamma vs error rate
ps_all_aggregate_for_K <- ps_all_merge[, lapply(.SD, mean), .SDcols = "in_ci.mathematical", by = .(K, iters, pop)]
FS1 <- ggplot(ps_all_aggregate_for_K, aes(x = K, y = in_ci.mathematical*100)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(iters~pop) +
  theme_bw() +
  # khroma::scale_color_batlow(discrete = TRUE, reverse = TRUE) +
  # khroma::scale_fill_batlow(discrete = TRUE, reverse = TRUE) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab(parse(text = "gamma")) +
  ylab("% estimates in CI")

# Figure S2: maf vs error rate
ps_all_aggregate_for_af <- ps_all_merge[, lapply(.SD, mean), .SDcols = "in_ci.mathematical", by = .(af, iters, pop)]
FS2 <- ggplot(ps_all_aggregate_for_af, aes(x = af, y = in_ci.mathematical*100)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(iters~pop) +
  theme_bw() +
  # khroma::scale_color_batlow(discrete = TRUE, reverse = TRUE) +
  # khroma::scale_fill_batlow(discrete = TRUE, reverse = TRUE) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab("Minor Allele Frequency") +
  ylab("% estimates in CI")

f3a <- ggplot(ps_all_merge, aes(x = K, y = diff, color = in_ci.mathematical)) +
  geom_point() +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab(parse(text = "gamma")) +
  ylab(bquote(italic(P*"("*S[jq]*")"[E]) - italic(P*"("*S[jq]*")"[O]))) +
  guides(color = guide_legend(title = "In 95% CI"))

f3b <- ggplot(ps_all_merge, aes(x = af, y = diff, color = in_ci.mathematical)) +
  geom_point() +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab("Minor Allele Frequency") +
  ylab(bquote(italic(P*"("*S[jq]*")"[E]) - italic(P*"("*S[jq]*")"[O])))

f3c <- ggplot(ps_all_merge, aes(x = iters, y = diff, color = in_ci.mathematical)) +
  geom_point() +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], 
                                   angle = 90, vjust = .5),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab("Number of Simulated Draws") +
  ylab(bquote(italic(P*"("*S[jq]*")"[E]) - italic(P*"("*S[jq]*")"[O])))

@@

save_plot("Figure3.pdf", f3, base_height = 11, base_width = 15)
```
# Figure 4 Nseg vs parameters

@@

f4a <- ggplot(ns_all[iters == 10000,], aes(x = K, y = nseg)) +
  geom_errorbar(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = K, ymin = lower, ymax = upper), color = "#DDAA33", size = 1, 
            position = position_nudge(x = 3.5),
            inherit.aes = FALSE, width = 2) +
  stat_ydensity(aes(group = K), draw_quantiles = c(.025, .975), scale = "width", bw = .4,
                fill = NA, width = 6) +
  facet_wrap(~pop) +
  theme_bw() + 
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(E*"("*N[S]*")") - italic(N[S,observed]))) +
  xlab(bquote(gamma))

f4b <- ggplot(ns_all[K == 50,], aes(x = iters, y = nseg)) +
  geom_errorbar(data = unique(ns_all[K == 50,c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = iters, ymin = lower, ymax = upper), color = "#DDAA33", size = 1, 
            position = position_nudge(x = 350),
            inherit.aes = FALSE, width = 200) +
  stat_ydensity(aes(group = iters), draw_quantiles = c(.025, .975), scale = "width", bw = .4,
                fill = NA, width = 600) +
  facet_wrap(~pop) +
  theme_bw() + 
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(E*"("*N[S]*")") - italic(N[S,observed]))) +
  xlab("Number of Simulated Draws")

@@

```{r}

#===============plot all of the observed values vs the estimated value for the sums=============
# plot the estimated prediction interval vs the observations and the confint from the simultations

#==========others==================

# variances, per locus
vars <- rbind(cbind.data.frame(estimated = vseg1, 
                               observed = matrixStats::rowVars(seg1),
                               pop = paste0("n = ", n1/2),
                               af = allele_frequencies),
              cbind.data.frame(estimated = vseg2, 
                               observed = matrixStats::rowVars(seg2),
                               pop = paste0("n = ", n2/2),
                               af = allele_frequencies))
ggplot(vars, aes(x = observed, y = estimated, color = af)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~pop) +
  theme_bw() +
  khroma::scale_color_batlow()

# variances, overall
overall_vars <- rbind(cbind.data.frame(estimated = sum(vseg1),
                                       observed = var(msum1),
                                       pop = paste0("n = ", n1/2)),
                      cbind.data.frame(estimated = sum(vseg2),
                                       observed = var(msum2),
                                       pop = paste0("n = ", n2/2)))
```

>>>>

F1data$in_ci <- ifelse(F1data$in_ci, "Yes", "No")

f1 <- ggplot(F1data[F1data$source == "Mathematical",],
             aes(x = af, y = p)) +
  geom_point(aes(color = in_ci), size = 2.5) +
  geom_errorbar(aes(ymax = upper, ymin = lower)) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  scale_color_manual(values = colors) +
  guides(color = guide_legend(title = "In 95% CI")) +
  ylab(bquote(italic(hat(P)*"("*S[jq]*")"))) +
  xlab("Minor Allele Frequency") +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2]))

@@

# Figure 3: Distribution of Nseg vs Eseg for four runs
Note that the label are flipped here: this produces figure 3.

@@

K20_data <- which(ks == 20 & n_iters == 10000)
F1data_K20 <- prep_f1(pseg1 = pseg1$K_20, 
                       pseg2 = pseg2$K_20, 
                       mpseg1 = res_files[[K20_data]]$mpseg1,
                       mpseg2 = res_files[[K20_data]]$mpseg2,
                       n1 = n1,
                       n2 = n2)

@@

K20_data <- which(ks == 20 & n_iters == 10000)
F2data_K20 <- prep_f2(seg1 = res_files[[K20_data]]$seg1, 
                       seg2 = res_files[[K20_data]]$seg2, 
                       vseg1 = vseg1$K_20,
                       vseg2 = vseg2$K_20,
                       F1data = F1data_K20,
                       n1 = n1,
                       n2 = n2)

F2data_K10$sum_tab$K <- "gamma * ' = 10'"
F2data_K20$sum_tab$K <- "gamma * ' = 20'"
F2data_K10$all_mcmc_sums$K <- "gamma * ' = 10'"
F2data_K20$all_mcmc_sums$K <- "gamma * ' = 20'"
F2data_K10$pi_tab$K <- "gamma * ' = 10'"
F2data_K20$pi_tab$K <- "gamma * ' = 20'"

F2data_sums <- rbind(F2data_K10$sum_tab, F2data_K20$sum_tab)
F2data_sums$pop <- gsub("n", "N", F2data_sums$pop)
F2data_sums$pop <- paste0("'", F2data_sums$pop, "'")

F2data_mcmcs <- rbind(F2data_K10$all_mcmc_sums, F2data_K20$all_mcmc_sums)
F2data_mcmcs$pop <- gsub("n", "N", F2data_mcmcs$pop)
F2data_mcmcs$pop <- paste0("'", F2data_mcmcs$pop, "'")

F2data_pi <- rbind(F2data_K10$pi_tab, F2data_K20$pi_tab)
F2data_pi$pop <- gsub("n", "N", F2data_pi$pop)
F2data_pi$pop <- paste0("'", F2data_pi$pop, "'")

F2data_mcmcs <- as.data.table(F2data_mcmcs)
levs <- unique(F2data_mcmcs[,c("pop", "K")])
F2data_densities <- vector("list", nrow(levs))

for(i in 1:nrow(levs)){
  d <- density(F2data_mcmcs[K == levs$K[i] & pop == levs$pop[i],]$nseg)
  q <- quantile(F2data_mcmcs[K == levs$K[i] & pop == levs$pop[i],]$nseg, c(0.025,0.975))
  F2data_densities[[i]] <- data.table(x = d$x, y = d$y, K = levs$K[i], pop = levs$pop[i])
  F2data_densities[[i]]$quant <- factor(findInterval(F2data_densities[[i]]$x, q))
}

F2data_densities <- rbindlist(F2data_densities)

f2 <- ggplot(F2data_densities, aes(x = x, y = y)) +
  geom_line() +
  geom_ribbon(aes(ymin = 0, ymax = y, fill = quant), show.legend = FALSE) +
  geom_vline(data = F2data_sums, aes(xintercept = nseg), color = colors[1]) +
  geom_vline(data = F2data_pi, aes(xintercept = lower), linetype = "dashed", color = colors[2]) +
  geom_vline(data = F2data_pi, aes(xintercept = upper), linetype = "dashed", color = colors[2]) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c("#004488", "#ffffff", "#004488")) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank()) +
  xlab(bquote(italic(N[S]))) +
  ylab("Density")

ggsave("Figure3.pdf", f2, height = 10, width = 15)

@@

# Figure 2: var vs difference between estimate and mean of simulations for mcmc and k
Note that the labels are flipped here, this produces figure 2

@@

# Figure S1: gamma vs error rate
ps_all_aggregate_for_K <- ps_all_merge[, lapply(.SD, mean), .SDcols = "in_ci.mathematical", by = .(K, iters, pop)]
FS1 <- ggplot(ps_all_aggregate_for_K, aes(x = K, y = in_ci.mathematical*100)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(iters~pop) +
  theme_bw() +
  # khroma::scale_color_batlow(discrete = TRUE, reverse = TRUE) +
  # khroma::scale_fill_batlow(discrete = TRUE, reverse = TRUE) +
  theme(axis.text = element_text(size = t.sizes[2] - 2),
        axis.title = element_text(size = t.sizes[1] - 2),
        strip.text = element_text(size = t.sizes[1] - 2),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1] - 2),
        legend.text = element_text(size = t.sizes[2] - 2)) +
  xlab(parse(text = "gamma")) +
  ylab("% estimates in CI")

save_plot("FigureS1.pdf", FS1, base_height = 10, base_width = 15)

# # Figure S2: maf vs error rate
# ps_all_aggregate_for_af <- ps_all_merge[, lapply(.SD, mean), .SDcols = "in_ci.mathematical", by = .(af, iters, pop)]
# FS2 <- ggplot(ps_all_aggregate_for_af, aes(x = af, y = in_ci.mathematical*100)) +
#   geom_point() +
#   geom_smooth(method = "lm", se = FALSE) +
#   facet_grid(iters~pop) +
#   theme_bw() +
#   # khroma::scale_color_batlow(discrete = TRUE, reverse = TRUE) +
#   # khroma::scale_fill_batlow(discrete = TRUE, reverse = TRUE) +
#   theme(axis.text = element_text(size = t.sizes[2]),
#         axis.title = element_text(size = t.sizes[1]),
#         strip.text = element_text(size = t.sizes[1]),
#         strip.background = element_blank(),
#         legend.title = element_text(size = t.sizes[1]),
#         legend.text = element_text(size = t.sizes[2])) +
#   xlab("Minor Allele Frequency") +
#   ylab("% estimates in CI")

ps_all_merge[,in_ci.mathematical := ifelse(in_ci.mathematical, "Yes", "No")]
ps_all_merge[,in_ci.mathematical := factor(in_ci.mathematical, c("Yes", "No"))]
f3a <- ggplot(ps_all_merge, aes(x = K, y = diff, color = in_ci.mathematical, group = in_ci.mathematical)) +
  geom_point(position = position_dodge(4)) +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab(parse(text = "gamma")) +
  ylab(bquote(italic(hat(P)*"("*S[jq]*")") - italic(P*"("*S[jq]*")"))) +
  guides(color = guide_legend(title = "In 95% CI"))

f3b <- ggplot(mapping = aes(x = af, y = diff, color = in_ci.mathematical)) +
  geom_point(data = ps_all_merge[in_ci.mathematical == "Yes",]) +
  geom_point(data = ps_all_merge[in_ci.mathematical == "No",]) +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_blank(),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab("Minor Allele Frequency") +
  ylab(bquote(italic(hat(P)*"("*S[jq]*")") - italic(P*"("*S[jq]*")")))

f3c <- ggplot(ps_all_merge, aes(x = iters, y = diff, color = in_ci.mathematical, group = in_ci.mathematical)) +
  geom_point(position = position_dodge(400)) +
  theme_bw() +
  facet_grid(~pop) +
  khroma::scale_color_highcontrast() +
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_blank(),
        axis.text.x = element_text(size = t.sizes[2], 
                                   angle = 90, vjust = .5),
        strip.background = element_blank(),
        legend.title = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  xlab("Number of Simulated Draws") +
  ylab(bquote(italic(hat(P)*"("*S[jq]*")") - italic(P*"("*S[jq]*")")))

@@

save_plot("Figure2.pdf", f3, base_height = 11, base_width = 15)
```
# Figure 4 Nseg vs parameters

@@

f4a <- ggplot(ns_all[iters == 10000,], aes(x = K, y = nseg)) +
  geom_errorbar(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = K + 3.7, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 2) +
  geom_point(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = K + 3.7, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = K), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 6) +
  facet_wrap(~pop) +
  scale_y_continuous(breaks = seq(40, 100, by = 10), limits = c(40, 100)) +
  theme_bw() + 
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(N[S]))) +
  xlab(bquote(gamma))

f4b <- ggplot(ns_all[K == 50,], aes(x = iters, y = nseg)) +
  geom_errorbar(data = unique(ns_all[K == 50,c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = iters + 370, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 200) +
  geom_point(data = unique(ns_all[K == 50, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = iters + 370, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = iters), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 600) +
  facet_wrap(~pop) +
  theme_bw() + 
  scale_y_continuous(breaks = seq(40, 100, by = 5), limits = c(80, 100)) +
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.text = element_blank(),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(N[S]))) +
  xlab("Number of Simulated Draws")

f4 <- plot_grid(f4a, f4b, ncol = 1, axis = "l", align = "l")
save_plot("Figure4.pdf", f4, base_height = 11, base_width = 15)

# S2
ns_all_agg <- ns_all[,lapply(.SD,mean), .SDcols = "nseg", by = c("ENs", "pop", "K", "iters", "i")]
levs <- paste0("Sims = ", sort(unique(ns_all_agg$iters)))
ns_all_agg$iters <- factor(paste0("Sims = ", ns_all_agg$iters), levels = levs)
ns_all_agg$pop <- gsub("n", "N", ns_all_agg$pop)
ns_all_agg$stat <- "Mean"

ns_all_agg_med <- ns_all[,lapply(.SD,median), .SDcols = "nseg", by = c("ENs", "pop", "K", "iters", "i")]
levs <- paste0("Sims = ", sort(unique(ns_all_agg_med$iters)))
ns_all_agg_med$iters <- factor(paste0("Sims = ", ns_all_agg_med$iters), levels = levs)
ns_all_agg_med$pop <- gsub("n", "N", ns_all_agg_med$pop)
ns_all_agg_med$stat <- "Median"

ns_all_agg <- rbind(ns_all_agg, ns_all_agg_med)
FS2 <- ggplot(ns_all_agg, aes(x = K, y = ENs - nseg, color = pop)) +
  geom_point() +
  facet_grid(stat~iters) +
  khroma::scale_color_highcontrast() +
  geom_hline(yintercept = 0) +
  theme_bw() +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.background = element_blank(),
        strip.text = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(E(N[S])) * " - " * italic(N[S,observed]))) +
  xlab(bquote(gamma)) +
  guides(color = guide_legend(title = "Population"))

save_plot("FigureS2.pdf", FS2, base_height = 10, base_width = 15)

@@
